\documentclass[11pt,a4paper]{article}
\usepackage[a4paper,left=0.8in,right=0.8in,top=0.8in,bottom=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{fontawesome5}
\usepackage{roboto}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{hyperref}

% Define colors
\definecolor{sidecolor}{HTML}{2A3B4C}
\definecolor{mainblue}{HTML}{1976D2}
\definecolor{lightblue}{HTML}{64B5F6}
\definecolor{headergray}{HTML}{37474F}
\definecolor{textgray}{HTML}{424242}
\definecolor{accent}{HTML}{26A69A}

% Hyperlinks setup
\hypersetup{
    colorlinks=true,
    urlcolor=mainblue,
    linkcolor=mainblue
}

% Remove page numbers
\pagestyle{empty}

% Custom sidebar section
\newcommand{\sidebarsection}[1]{
    \vspace{0.3cm}
    \textbf{\textcolor{white}{\large #1}}
    \vspace{0.1cm}
    
    \textcolor{lightblue}{\rule{\linewidth}{1pt}}
    \vspace{0.2cm}
}

% Custom main section
\newcommand{\mainsection}[1]{
    \vspace{0.3cm}
    \textbf{\textcolor{headergray}{\Large #1}}
    \vspace{0.1cm}
    
    \textcolor{mainblue}{\rule{\linewidth}{1pt}}
    \vspace{0.25cm}
}

% Custom command for job entry
\newcommand{\jobentry}[4]{
    \textbf{\textcolor{mainblue}{#1}} \hfill \textbf{#2}\\
    \textit{#3} \hfill \textit{#4}\\
    \vspace{0.1cm}
}

% Skill bar command
\newcommand{\skillbar}[2]{
    \textbf{#1} \hfill
    \begin{tikzpicture}[baseline]
        \fill[gray!30] (0,0) rectangle (5,0.15);
        \fill[accent] (0,0) rectangle (#2,0.15);
    \end{tikzpicture}\\
    \vspace{0.1cm}
}

\begin{document}

% Two-column layout with sidebar
\noindent
\begin{tikzpicture}[remember picture, overlay]
    \fill[sidecolor] (current page.north west) rectangle ([xshift=2.7in] current page.south west);
\end{tikzpicture}

\begin{minipage}[t]{0.3\textwidth}
    \begin{center}
        \vspace{0.4cm}
        \textcolor{white}{\Huge\textbf{Kelvin}}\\
        \textcolor{white}{\Huge\textbf{Odi}}\\
        \vspace{0.3cm}
        \textcolor{lightblue}{\rule{0.8\linewidth}{1pt}}\\
        \vspace{0.3cm}
        \textcolor{white}{\large Digital Process Engineer}\\
        \textcolor{white}{\& Software Developer}
    \end{center}
    
    \vspace{0.8cm}
    \sidebarsection{CONTACT}
    \begin{flushleft}
        \textcolor{white}{
        \faEnvelope\ \ kelvinetoma95@gmail.com}\\
        \vspace{0.1cm}
        \textcolor{white}{
        \faPhone\ \ +234 913 712 4272}\\
        \vspace{0.1cm}
        \textcolor{white}{
        \faGithub\ \ github.com/kellytomi}\\
        \vspace{0.1cm}
        \textcolor{white}{
        \faMapMarkerAlt\ \ Remote (WAT timezone)}
    \end{flushleft}
    
    \sidebarsection{TECHNICAL SKILLS}
    \textcolor{white}{
        \skillbar{Next.js/React}{4.5}
        \skillbar{Flutter/Dart}{4.2}
        \skillbar{CRM Integration}{4.8}
        \skillbar{Process Automation}{4.7}
        \skillbar{Make/Zapier}{4.9}
        \skillbar{Document Systems}{4.5}
        \skillbar{Node.js}{3.8}
        \skillbar{Firebase/Supabase}{4.0}
    }
    
    \sidebarsection{TOOLS \& PLATFORMS}
    \begin{flushleft}
        \textcolor{white}{
            \textbullet\ PandaDoc, Typeform\\
            \textbullet\ Monday.com, HubSpot\\
            \textbullet\ Zoho, Copper CRM\\
            \textbullet\ Airtable, Google Sheets\\
            \textbullet\ Make, Zapier\\
            \textbullet\ Canva, Dropbox\\
            \textbullet\ Notion, Trello
        }
    \end{flushleft}
    
    \sidebarsection{EDUCATION}
    \textcolor{white}{
        \textbf{Lead City University}\\
        \small Ibadan, Nigeria\\
        BSc Software Engineering\\
        2024 - 2028 (In Progress)
    }
    
    \vspace{0.3cm}
    \textcolor{white}{
        \textbf{Certifications}\\
        \small Flutter Development Bootcamp\\
        \small Zapier Certified Expert\\
        \small Make (Integromat) Advanced User\\
        \small PandaDoc Implementation Specialist
    }
\end{minipage}
\hfill
\begin{minipage}[t]{0.65\textwidth}
    \vspace{0.4cm}
    \mainsection{PROFESSIONAL SUMMARY}
    
    \textcolor{textgray}{Results-driven Digital Process Engineer and Software Developer with proven experience in automating business operations, building web/mobile apps, and streamlining workflows. Adept at solving technical challenges across CRMs, document platforms, and third-party integrations. Skilled in Flutter, Next.js, and automation stacks like Make, Zapier, and PandaDoc. Known for delivering client-centric solutions that boost efficiency, reduce manual effort, and create seamless user experiences.}
    
    \mainsection{PROFESSIONAL EXPERIENCE}
    
    \jobentry{Fxsion Studios}{Remote}
    {Founder / CRM \& Automation Specialist / Flutter Developer}{Feb 2023 -- Present}
    
    \begin{itemize}[leftmargin=1.5em, itemsep=2pt, label=\textcolor{mainblue}{\footnotesize\faAngleRight}]
        \item Developed web and mobile applications for clients using Flutter and Next.js, focusing on performance and responsiveness.
        \item Provided ongoing technical support and website maintenance for WordPress clients, including plugin audits and bug fixes.
        \item Designed and troubleshooted CRM workflows using HubSpot, Monday.com, Zoho, and Copper.
        \item Built document automation flows using PandaDoc integrated with CRMs, Typeform, and Google Sheets.
        \item Created reusable documentation, training resources, and handover guides.
    \end{itemize}
    
    \vspace{0.3cm}
    \jobentry{Upwork Clients (Various Industries)}{Remote}
    {Technical Support \& Workflow Consultant}{Jul 2022 -- Present}
    
    \begin{itemize}[leftmargin=1.5em, itemsep=2pt, label=\textcolor{mainblue}{\footnotesize\faAngleRight}]
        \item Converted sales documents into branded, dynamic templates using PandaDoc.
        \item Migrated CRM systems (e.g., Zoho, HubSpot) with full data and process alignment.
        \item Built Make/Zapier automations involving Dropbox, Google Sheets, and Canva for asset management and reporting.
        \item Created training videos, Loom walkthroughs, and tracked feedback using ClickUp/Monday.
    \end{itemize}
    
    \vspace{0.3cm}
    \jobentry{Yacht Zero Inc.}{Remote}
    {Digital Process Engineer \& Automation Expert}{Apr 2024 -- Apr 2025}
    
    \begin{itemize}[leftmargin=1.5em, itemsep=2pt, label=\textcolor{mainblue}{\footnotesize\faAngleRight}]
        \item Led automation flows for brokers using Trello, PandaDoc, and Airtable triggers.
        \item Developed Airtable--Dropbox--Canva automations for marketing asset curation and yacht video breakdowns.
        \item Built API-integrated listing pages for the company website using YATCO.
        \item Generated structured documents, folders, and reports using Monday.com data.
        \item Supported CRM setup, database syncing, and automated client communication tools.
    \end{itemize}
    
    \mainsection{PROJECTS \& ACHIEVEMENTS}
    
    \begin{itemize}[leftmargin=1.5em, itemsep=5pt, label=\textcolor{mainblue}{\footnotesize\faCircle}]
        \item \textbf{Multi-Platform CRM Integration} — Developed a custom solution connecting HubSpot, PandaDoc, and Airtable for a fintech startup, reducing manual data entry by 85\%.
        
        \item \textbf{Automation Workflow Redesign} — Rebuilt a marketing agency's client onboarding process using Make and Zapier, cutting onboarding time from 2 weeks to 3 days.
        
        \item \textbf{Mobile App Development} — Created a Flutter-based inventory management application for iOS and Android with offline capabilities and cloud synchronization.
        
        \item \textbf{Document Generation System} — Implemented an automated document creation system for a legal services firm, generating compliant contracts from client data.
    \end{itemize}
    
    \mainsection{PROFESSIONAL DEVELOPMENT}
    
    \begin{itemize}[leftmargin=1.5em, itemsep=3pt, label=\textcolor{mainblue}{\footnotesize\faGraduationCap}]
        \item Contribute to automation community forums and knowledge bases
        \item Attend webinars on CRM integration and document automation best practices
        \item Participate in Flutter developer communities and contribute to open-source projects
        \item Stay current with API changes and integration opportunities across platforms
    \end{itemize}
\end{minipage}

\end{document} 